Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-14 WRITEUP/ms.tex
corresponding changes to ms

\begin{figure*}
\centering
\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16_larsons.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_larsons.png}
\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_alphavir.png}
\includegraphics[trim=5 5 8 8, clip, width=0.512\textwidth]{\figpath/ss16_PVE.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_PVE.png}
\caption{
Linewidth-size relation (top),
{\bf .... (middle), and blah blah (bottom)}
for MCs (star symbols)
identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right).
Star symbols are color-coded by the density thresholds ($n_{\rm cut}$).
\AP{ have not found a good clipping for the upper left panel}
\AP{please 1) increase a bit the size of the labels 2) put the legend only the right panels
3) add a text label to the upper left corner, to ditinguish between accreting and starburst stage
4) I would use a perceptually increasing colorbar to indicate the different cuts
5) legend for the cuts can be substituted by a colorbar axis to be shown as an inset in 1 of the panels or as a separate figure below the panels}
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16-28_larsons.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-larsons-highncut.png}
\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16-28_alphavir.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
\includegraphics[trim=5 5 8 8, clip, width=0.512\textwidth]{\figpath/ss16-28_PVE.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-PVE-highncut.png}
\caption{
Same as \Fig{larsons_single}, except star symbols are showing MCs identified across all evolutionary 
stages traced in our simulation, which are color-coded by the SFR of \flower in those stages. 
Left panels show MCs identified using a low $n_{\rm cut}$ \DL{check how low?} 
and right panels show MCs identified using a high $n_{\rm cut}$ \DL{check how high?}.
\label{fig:alpha16-28}}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[trim=30 30 0 0, clip, width=1.1\textwidth]{\figpath/3by2_clumpProp_ss16-27.pdf}
\caption{
Linewidth-size relation (top),
{\bf .... (middle), and blah blah (bottom)}
for MCs (star symbols)
identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right).
Star symbols are color-coded by the density thresholds ($n_{\rm cut}$). \DL{some missing character after downloading 
to local.. only the case if we saved them as .pdf.. interestingly but not the case if I save as .png}
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=20 20 0 0, clip, width=1.1\textwidth]{\figpath/3by2_clumpProp_allss.png}
\caption{
Same as \Fig{larsons_single}, except star symbols are showing MCs identified across all evolutionary 
stages traced in our simulation, which are color-coded by the SFR of \flower in those stages. 
Left panels show MCs identified using a low $n_{\rm cut}$\eq0.53\,\cc
and right panels show MCs identified using a high $n_{\rm cut}$\eq19\,\cc.
\label{fig:alpha16-28}}
\end{figure*}
